InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
edited citation

>>>>

Another image generative model is \textbf{midjourney} \cite{midjourney}. This model was created by an identically named and independent research lab. It can synthesize images from textual descriptions. Midjourney tends to generate surrealistic images and is popular among artists. It uses modern deep learning methods to create high-quality images.

\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding. Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation. \cite{imagen, saharia2022photorealistic}
